\renewcommand\bibname{References}
\begin{thebibliography}{9}
\bibitem{guardian}
The Guardian. (2013). \textit{You think Facebook is free? Well, it'll only cost you your private life}. Available from: \\\texttt{http://www.theguardian.com/commentisfree/2013/dec/29/observer-editorial-digital\--privacy} [Accessed 20th Jan. 2016]

\bibitem{bluekai}
Oracle BlueKai Platform/Exchange FAQs. Available from:
\\\texttt{https://docs.oracle.com/cloud/latest/daasmarketing\_gs/DSMKT/GUID-418EDA59\--1BD9-40F6-9D57-DD7C266555FF.htm\#DSMKT3616} [Accessed 24th Jan. 2016]

\bibitem{sweeney}
Latanya Sweeney. (2000) \textit{Simple Demographics Often Identify People Uniquely}. Available from: \texttt{http://dataprivacylab.org/projects/identifiability/paper1.pdf} [Accessed 20th Jan. 2016]

\bibitem{enigma}
Guy Zyskind, Oz Nathan, Alex 'Sandy' Pentland. \textit{Enigma: Decentralized Computation Platform with Guaranteed Privacy}. Available from:
\\\texttt{http://enigma.media.mit.edu/enigma\_full.pdf}. [Accessed 24th Jan. 2016]

\bibitem{chord}
Ion Stoica, Robert Morris, David Karger, M. Frans Kaashoek, Hari Balakrishnan. (2001) \textit{Chord: A Scalable Peer-to-peer Lookup Service for Internet Applications}. Available from:
\\\texttt{https://pdos.csail.mit.edu/papers/chord\:sigcomm01/chord\_sigcomm.pdf}. [Accessed 24th Jan. 2016]

\bibitem{datalocation}
Yves-Alexandre de Montjoye, César A. Hidalgo, Michel Verleysen, Vincent D. Blondel. (2013) \textit{Unique in the Crowd: The privacy bounds of human mobility}. Available from: \\
\texttt{http://www.nature.com/articles/srep01376} [Accessed 24th Jan. 2016]

\bibitem{popathesis}
Raluca A. Popa. (2009) \textit{Provable and Practical Location Privacy for Vehicular and Mobile Systems}. Available from:
\\\texttt{http://eecs.berkeley.edu/\~raluca/popa-thesis.pdf} [Accessed 28th Jan. 2016]

\bibitem{privstats}
Raluca Ada Popa, Andrew J. Blumberg, Hari Balakrishnan, Frank H. Li. (2011) \textit{Privacy and Accountability for Location-based Aggregate Statistics}. Available from:
\\\texttt{https://www.ma.utexas.edu/users/blumberg/privaggs.pdf}
[Accessed 28th Jan. 2016]

\bibitem{louislesterpierre}
Ge Zhong, Ian Goldberg, Urs Hengartner. (2007) \textit{Louis, Lester and Pierre: Three Protocols for Location Privacy}. Available from:
\\\texttt{https://cs.uwaterloo.ca/\~uhengart/publications/pet07.pdf}
[Accessed 28th Jan. 2016]

\bibitem{quantifylocationprivacy}
Reza Shokri, George Theodorakopoulos, Jean-Yves Le Boudec, Jean-Pierre Hubaux . (2011) \textit{Quantifying Location Privacy}. Available from:
\\\texttt{http://www.ieee-security.org/TC/SP2011/PAPERS/2011/paper016.pdf} [Accessed 28th Jan. 2016] 

\bibitem{differentialprivacy}
Cynthia Dwork. (2008) \textit{Differential Privacy: A Survey of Results}. Available from:
\\\texttt{http://research.microsoft.com/pubs/74339/dwork\_tamc.pdf} [Accessed 28th Jan. 2016]


\bibitem{facebook}
General Account Settings of Facebook - \textit{Download a copy of your Facebook data} option (2016). Available from:
\\\texttt{https://www.facebook.com/settings} [Accessed 24th Jan. 2016]

\bibitem{facebookprivacy}
Facebook User Data policy (2016). Available from: 
\\\texttt{https://www.facebook.com/about/privacy} [Accessed 28th Jan. 2016]

\bibitem{howmuchdata}
George Simos. (2015) \textit{How Much Data Is Generated Every Minute On Social Media?}. Available from:
\\\texttt{http://wersm.com/how-much-data-is-generated-every-minute-on-social-media/} [Accessed 28th Jan. 2016]

%\bibitem{petridish}
%Michael Szell, Roberta Sinatra, Giovanni Petri, Stefan Thurner, Vito Latora. (2012) \texttt{Understanding Mobility in a Social Petri Dish}. Available from:
%\\\texttt{http://www.nature.com/articles/srep00457?trendmd-shared=0}

%\bibitem{zcash}
%Andy Greenberg. (2016) \textit{Zcash, an Untraceable Bitcoin Alternative, Launches in Alpha}. Available from:
%\\\texttt{http://www.wired.com/2016/01/zcash-an-untraceable-bitcoin-alternative-launches-in-alpha/}

\bibitem{datacoup}
DataCoup (2016). Available from: \texttt{https://datacoup.com/} [Accessed 24th Jan. 2016]

\bibitem{citizenme}
CitizenMe (2015). Available from: \texttt{http://www.citizenme.com/} [Accessed 24th Jan. 2016]

\bibitem{peopleio}
People.io (2016). Available form: \texttt{https://people.io/} [Accessed 24th Jan. 2016]

\bibitem{digime}
DigiMe (2016). Available from:
\texttt{https://get.digi.me/} [Accessed 24th Jan. 2016]

\bibitem{cryptdb}
Raluca Ada Popa, Catherine M. S. Redfield, Nickolai Zeldovich, Hari Balakrishnan . (2011) \textit{CryptDB: Protecting Confidentiality with Encrypted Query Processing}. Available from: 
\\\texttt{http://people.csail.mit.edu/nickolai/papers/raluca-cryptdb.pdf} [Accessed 29th Jan. 2016]

\bibitem{smpc}
Yehuda Lindell, Benny Pinkas. (2009) \textit{Secure Multiparty Computation for Privacy-Preserving Data Mining}. Available from:
\\\texttt{http://repository.cmu.edu/cgi/viewcontent.cgi?article=1004\&context=jpc} [Accessed 29th Jan. 2016]

\end{thebibliography}
